### 2022-02-28 manuscript.tex
Delete 07.delete-me.md [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/b22eac44e470f1d266e862d8e4178c003f96a490.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/b22eac44e470f1d266e862d8e4178c003f96a490/checks
https://github.com/scherzerthesis/thesis/actions/runs/1911694727

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/65182116ec81c01b93395e140fdfd24b14753788/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/65182116ec81c01b93395e140fdfd24b14753788}{scherzerthesis/thesis@6518211}
on February 28, 2022.

@@

This manuscript is a template (aka ``rootstock'') for \href{https://manubot.org/}{Manubot}, a tool for writing scholarly manuscripts.
Use this template as a starting point for your manuscript.

The rest of this document is a full list of formatting elements/features supported by Manubot.
Compare the input (\texttt{.md} files in the \texttt{/content} directory) to the output you see below.

\hypertarget{basic-formatting}{%
\subsection{Basic formatting}\label{basic-formatting}}

\textbf{Bold} \textbf{text}

{Semi-bold text}

{Centered text}

{Right-aligned text}

\emph{Italic} \emph{text}

Combined \emph{italics and \textbf{bold}}

\sout{Strikethrough}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Ordered list item
\item
  Ordered list item

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \tightlist
  \item
    Sub-item
  \item
    Sub-item

    \begin{enumerate}
    \def\labelenumiii{\roman{enumiii}.}
    \tightlist
    \item
      Sub-sub-item
    \end{enumerate}
  \end{enumerate}
\item
  Ordered list item

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \tightlist
  \item
    Sub-item
  \end{enumerate}
\end{enumerate}

\begin{itemize}
\tightlist
\item
  List item
\item
  List item
\item
  List item
\end{itemize}

subscript: H\textsubscript{2}O is a liquid

superscript: 2\textsuperscript{10} is 1024.

\href{https://www.google.com/search?q=superscript+generator}{unicode superscripts}⁰¹²³⁴⁵⁶⁷⁸⁹

\href{https://www.google.com/search?q=superscript+generator}{unicode subscripts}₀₁₂₃₄₅₆₇₈₉

A long paragraph of text.
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Putting each sentence on its own line has numerous benefits with regard to \href{https://asciidoctor.org/docs/asciidoc-recommended-practices/\#one-sentence-per-line}{editing} and \href{https://rhodesmill.org/brandon/2012/one-sentence-per-line/}{version control}.

Line break without starting a new paragraph by putting\\
two spaces at end of line.

\hypertarget{document-organization}{%
\subsection{Document organization}\label{document-organization}}

Document section headings:

\hypertarget{heading-1}{%
\section{Heading 1}\label{heading-1}}

\hypertarget{heading-2}{%
\subsection{Heading 2}\label{heading-2}}

\hypertarget{heading-3}{%
\subsubsection{Heading 3}\label{heading-3}}

\hypertarget{heading-4}{%
\paragraph{Heading 4}\label{heading-4}}

\hypertarget{heading-5}{%
\subparagraph{Heading 5}\label{heading-5}}

Heading 6

\hypertarget{a-heading-centered-on-its-own-printed-page}{%
\subsubsection{A heading centered on its own printed page}\label{a-heading-centered-on-its-own-printed-page}}

Horizontal rule:

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\texttt{Heading\ 1}'s are recommended to be reserved for the title of the manuscript.

\texttt{Heading\ 2}'s are recommended for broad sections such as \emph{Abstract}, \emph{Methods}, \emph{Conclusion}, etc.

\texttt{Heading\ 3}'s and \texttt{Heading\ 4}'s are recommended for sub-sections.

\hypertarget{links}{%
\subsection{Links}\label{links}}

Bare URL link: \url{https://manubot.org}

\href{https://manubot.org}{Long link with lots of words and stuff and junk and bleep and blah and stuff and other stuff and more stuff yeah}

\href{https://manubot.org}{Link with text}

\href{https://manubot.org}{Link with hover text}

\href{https://manubot.org}{Link by reference}

\hypertarget{citations}{%
\subsection{Citations}\label{citations}}

Citation by DOI (Himmelstein \emph{et al.}, 2018).

Citation by PubMed Central ID (Beaulieu-Jones and Greene, 2017).

Citation by PubMed ID (Heaven, 2019).

Citation by Wikidata ID (S, 2018).

Citation by ISBN (Suber, 2012).

Citation by URL (Himmelstein \emph{et al.}, 2020).

Citation by alias (Ching \emph{et al.}, 2018).

Multiple citations can be put inside the same set of brackets (Himmelstein \emph{et al.}, 2018; Ching \emph{et al.}, 2018; Suber, 2012).
Manubot plugins provide easier, more convenient visualization of and navigation between citations (Himmelstein \emph{et al.}, 2019; Heaven, 2019; Beaulieu-Jones and Greene, 2017; Ching \emph{et al.}, 2018).

Citation tags (i.e.~aliases) can be defined in their own paragraphs using Markdown's reference link syntax:

\hypertarget{referencing-figures-tables-equations}{%
\subsection{Referencing figures, tables, equations}\label{referencing-figures-tables-equations}}

Figure \ref{fig:square-image}

Figure \ref{fig:wide-image}

Figure \ref{fig:tall-image}

Figure \ref{fig:vector-image}

Table \ref{tbl:bowling-scores}

Equation \ref{eq:regular-equation}

Equation \ref{eq:long-equation}

\hypertarget{quotes-and-code}{%
\subsection{Quotes and code}\label{quotes-and-code}}

\begin{quote}
Quoted text
\end{quote}

\begin{quote}
Quoted block of text

Two roads diverged in a wood, and I---\\
I took the one less traveled by,\\
And that has made all the difference.
\end{quote}

Code \texttt{in\ the\ middle} of normal text, aka \texttt{inline\ code}.

Code block with Python syntax highlighting:

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{from}\NormalTok{ manubot.cite.doi }\ImportTok{import}\NormalTok{ expand\_short\_doi}

\KeywordTok{def}\NormalTok{ test\_expand\_short\_doi():}
\NormalTok{    doi }\OperatorTok{=}\NormalTok{ expand\_short\_doi(}\StringTok{"10/c3bp"}\NormalTok{)}
    \CommentTok{\# a string too long to fit within page:}
    \ControlFlowTok{assert}\NormalTok{ doi }\OperatorTok{==} \StringTok{"10.25313/2524{-}2695{-}2018{-}3{-}vliyanie{-}enhansera{-}copia{-}i{-}insulyatora{-}gypsy{-}na{-}sintez{-}ernk{-}modifikatsii{-}hromatina{-}i{-}svyazyvanie{-}insulyatornyh{-}belkov{-}vtransfetsirovannyh{-}geneticheskih{-}konstruktsiyah"}
\end{Highlighting}
\end{Shaded}

Code block with no syntax highlighting:

\begin{verbatim}
Exporting HTML manuscript
Exporting DOCX manuscript
Exporting PDF manuscript
\end{verbatim}

\hypertarget{figures}{%
\subsection{Figures}\label{figures}}

\begin{figure}
\hypertarget{fig:square-image}{%
\centering
\includegraphics{https://github.com/manubot/resources/raw/15493970f8882fce22bef829619d3fb37a613ba5/test/square.png}
\caption{\textbf{A square image at actual size and with a bottom caption.}
Loaded from the latest version of image on GitHub.}\label{fig:square-image}
}
\end{figure}

\begin{figure}
\hypertarget{fig:wide-image}{%
\centering
\includegraphics{https://github.com/manubot/resources/raw/15493970f8882fce22bef829619d3fb37a613ba5/test/wide.png}
\caption{\textbf{An image too wide to fit within page at full size.}
Loaded from a specific (hashed) version of the image on GitHub.}\label{fig:wide-image}
}
\end{figure}

\begin{figure}
\hypertarget{fig:tall-image}{%
\centering
\includegraphics[width=\textwidth,height=3in]{https://github.com/manubot/resources/raw/15493970f8882fce22bef829619d3fb37a613ba5/test/tall.png}
\caption{\textbf{A tall image with a specified height.}
Loaded from a specific (hashed) version of the image on GitHub.}\label{fig:tall-image}
}
\end{figure}

\begin{figure}
\hypertarget{fig:vector-image}{%
\centering
\includegraphics[width=\textwidth,height=2.5in]{https://raw.githubusercontent.com/manubot/resources/main/test/vector.svg?sanitize=true}
\caption{\textbf{A vector \texttt{.svg} image loaded from GitHub.}
The parameter \texttt{sanitize=true} is necessary to properly load SVGs hosted via GitHub URLs.
White background specified to serve as a backdrop for transparent sections of the image.}\label{fig:vector-image}
}
\end{figure}

\hypertarget{tables}{%
\subsection{Tables}\label{tables}}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2308}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1923}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1923}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1923}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1923}}@{}}
\caption{A table with a top caption and specified relative column widths.
\label{tbl:bowling-scores}}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\emph{Bowling Scores}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Jane
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
John
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Alice
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Bob
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\emph{Bowling Scores}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Jane
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
John
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Alice
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Bob
\end{minipage} \\
\midrule
\endhead
Game 1 & 150 & 187 & 210 & 105 \\
Game 2 & 98 & 202 & 197 & 102 \\
Game 3 & 123 & 180 & 238 & 134 \\
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.0511}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2045}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1989}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1989}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.3466}}@{}}
\caption{A table too wide to fit within page.
\label{tbl:constant-digits}}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Digits 1-33
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Digits 34-66
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Digits 67-99
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Ref.
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Digits 1-33
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Digits 34-66
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Digits 67-99
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Ref.
\end{minipage} \\
\midrule
\endhead
pi & 3.14159265358979323846264338327950 & 288419716939937510582097494459230 & 781640628620899862803482534211706 & \href{https://www.piday.org/million/}{\texttt{piday.org}} \\
e & 2.71828182845904523536028747135266 & 249775724709369995957496696762772 & 407663035354759457138217852516642 & \href{https://apod.nasa.gov/htmltest/gifcity/e.2mil}{\texttt{nasa.gov}} \\
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}ccc@{}}
\caption{A table with merged cells using the \texttt{attributes} plugin.
}\tabularnewline
\toprule
& \textbf{Colors} & \\
\midrule
\endfirsthead
\toprule
& \textbf{Colors} & \\
\midrule
\endhead
\textbf{Size} & \textbf{Text Color} & \textbf{Background Color} \\
big & blue & orange \\
small & black & white \\
\bottomrule
\end{longtable}

\hypertarget{equations}{%
\subsection{Equations}\label{equations}}

A LaTeX equation:

\begin{equation}\int_0^\infty e^{-x^2} dx=\frac{\sqrt{\pi}}{2}\label{eq:regular-equation}\end{equation}

An equation too long to fit within page:

\begin{equation}x = a + b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z + 1 + 2 + 3 + 4 + 5 + 6 + 7 + 8 + 9\label{eq:long-equation}\end{equation}

\hypertarget{special}{%
\subsection{Special}\label{special}}

{WARNING} \emph{The following features are only supported and intended for \texttt{.html} and \texttt{.pdf} exports.}
\emph{Journals are not likely to support them, and they may not display correctly when converted to other formats such as \texttt{.docx}.}

\href{https://manubot.org}{Link styled as a button}

Adding arbitrary HTML attributes to an element using Pandoc's attribute syntax:

\leavevmode\vadjust pre{\hypertarget{some_id_1}{}}%
Manubot Manubot Manubot Manubot Manubot.
Manubot Manubot Manubot Manubot.
Manubot Manubot Manubot.
Manubot Manubot.
Manubot.

Adding arbitrary HTML attributes to an element with the Manubot \texttt{attributes} plugin (more flexible than Pandoc's method in terms of which elements you can add attributes to):

Manubot Manubot Manubot Manubot Manubot.
Manubot Manubot Manubot Manubot.
Manubot Manubot Manubot.
Manubot Manubot.
Manubot.

Available background colors for text, images, code, banners, etc:

\texttt{white}
\texttt{lightgrey}
\texttt{grey}
\texttt{darkgrey}
\texttt{black}
\texttt{lightred}
\texttt{lightyellow}
\texttt{lightgreen}
\texttt{lightblue}
\texttt{lightpurple}
\texttt{red}
\texttt{orange}
\texttt{yellow}
\texttt{green}
\texttt{blue}
\texttt{purple}

Using the \href{https://fontawesome.com/}{Font Awesome} icon set:

{ \textbf{Light Grey Banner}
useful for \emph{general information} - \href{https://manubot.org/}{manubot.org}}

{ \textbf{Blue Banner}
useful for \emph{important information} - \href{https://manubot.org/}{manubot.org}}

{ \textbf{Light Red Banner}
useful for \emph{warnings} - \href{https://manubot.org/}{manubot.org}}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-mSMVRkoc}{}}%
Beaulieu-Jones,B.K. and Greene,C.S. (2017) \href{https://doi.org/10.1038/nbt.3780}{Reproducibility of computational workflows is automated using continuous analysis}. \emph{Nat Biotechnol}, \textbf{35}, 342--346.

\leavevmode\vadjust pre{\hypertarget{ref-PZMP42Ak}{}}%
Ching,T. \emph{et al.} (2018) \href{https://doi.org/10.1098/rsif.2017.0387}{Opportunities and obstacles for deep learning in biology and medicine}. \emph{J. R. Soc. Interface.}, \textbf{15}, 20170387.

\leavevmode\vadjust pre{\hypertarget{ref-126Wi5Us4}{}}%
Heaven,D. (2019) \href{https://doi.org/10.1038/d41586-019-00447-9}{Bitcoin for the biological literature.} \emph{Nature}, \textbf{566}, 141--142.

\leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
Himmelstein,D.S. \emph{et al.} (2019) \href{https://doi.org/10.1371/journal.pcbi.1007128}{Open collaborative writing with Manubot}. \emph{PLoS Comput Biol}, \textbf{15}, e1007128.

\leavevmode\vadjust pre{\hypertarget{ref-1GGGHdsew}{}}%
Himmelstein,D.S. \emph{et al.} (2020) \href{https://greenelab.github.io/meta-review/}{Open collaborative writing with Manubot} Manubot.

\leavevmode\vadjust pre{\hypertarget{ref-IhliSZDo}{}}%
Himmelstein,D.S. \emph{et al.} (2018) \href{https://doi.org/10.7554/elife.32822}{Sci-Hub provides access to nearly all scholarly literature}. \emph{eLife}, \textbf{7}.

\leavevmode\vadjust pre{\hypertarget{ref-QhC8yJ7V}{}}%
S,cOAlition. (2018) \href{https://www.wikidata.org/wiki/Q56458321}{Plan S: Accelerating the transition to full and immediate Open Access to scientific publications}.

\leavevmode\vadjust pre{\hypertarget{ref-zBPP9YKu}{}}%
Suber,P. (2012) Open access MIT Press, Cambridge, Mass.

\end{CSLReferences}

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/b22eac44e470f1d266e862d8e4178c003f96a490/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/b22eac44e470f1d266e862d8e4178c003f96a490}{scherzerthesis/thesis@b22eac4}
on February 28, 2022.

@@

@@

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\end{CSLReferences}
